### 2018-08-23 Sections/classical_networking_protocols.tex
squeezing

There have been numerous approaches employed in the past for sharing communications links between multiple users\index{Shared communication channels}. This includes:
\begin{itemize}
	\item Channel-switching: an entire communications channel is designated for exclusive use by a given user. \index{Channel-switched networks}
	\item Packet-switching: data is divided into packets, which are routed independently by the network, being reconstructed by the recipient once all packets have been received.\index{Packet-switching}
	\item Time- or frequency-multiplexing: each user is designated a particular frequency spectrum or series of time-slots exclusively for their use. \index{Time-multiplexing}\index{Frequency-multiplexing}
	\item Code Division Multiple Access (CDMA): all users can broadcast over a channel simultaneously, and the construction of the coding technique enables demultiplexing of the distinct signals, despite their interference with one another.\index{Code Division Multiple Access (CDMA)}
	\item Ethernet: all users are free to broadcast\index{Broadcast networks} over a shared channel at will, and \textit{collision detection}\index{Collision detection} identifies when packets interfere, after which they are discarded and rebroadcast following a random waiting period, repeating until success.\index{Ethernet}
\end{itemize}

>>>>

\dropcap{T}{here} have been numerous approaches employed in the past for sharing communications links between multiple users\index{Shared communication channels}. This includes:
\begin{itemize}
	\item Channel-switching: an entire communications channel is designated for exclusive use by a given user. \index{Channel-switched networks}
	\item Packet-switching: data is divided into packets, which are routed independently by the network, being reconstructed by the recipient once all packets have been received.\index{Packet-switching}
	\item Time- or frequency-multiplexing: each user is designated a particular frequency spectrum or series of time-slots exclusively for their use. \index{Time-multiplexing}\index{Frequency-multiplexing}
	\item Code Division Multiple Access (CDMA): all users can broadcast over a channel simultaneously, and the construction of the coding technique enables demultiplexing of the distinct signals, despite their interference with one another.\index{Code Division Multiple Access (CDMA)}
	\item Ethernet: all users are free to broadcast\index{Broadcast networks} over a shared channel at will, and \textit{collision detection}\index{Collision detection} identifies when packets interfere, after which they are discarded and rebroadcast following a random waiting period, repeating until success.\index{Ethernet}
\end{itemize}

### 2018-08-23 Sections/costs_and_attributes_in_quantum_networks.tex
Minor touch ups
squeezing

We define the fidelity of two processes, the process fidelity \index{Fidelity} \cite{bib:Gilchrist05}, to be the fidelity between two identical copies of a state that have been evolved under each of those processes, minimised over all possible states. That is, it provides a lower bound on the fidelity between identical states evolved under the two processes. In the context of networking, where quality must be guaranteed, this definition is more appropriate than, say, the average case fidelity. Specifically,
\begin{align}
\mathcal{F}(\mathcal{E}_1,\mathcal{E}_2) = \mathrm{tr}\left( \sqrt{\chi_1^{1/2}\cdot\chi_2\cdot\chi_1^{1/2}}\right),
\end{align}
where $\chi_1$ and $\chi_2$ are the process matrices for $\mathcal{E}_1$ and $\mathcal{E}_2$.

@@

An alternate measure for the distance between two quantum states is the trace-norm distance\index{Trace-norm distance}, defined as,
\begin{align}
D(\hat\rho_1,\hat\rho_2) &= \frac{1}{2}\|\hat\rho_1 - \hat\rho_2\|_1 \nonumber\\
&= \frac{1}{2}\sum_i |\lambda_i|,
\end{align}
where $\lambda_i$ are the eigenvalues of \mbox{$\hat\rho_1-\hat\rho_2$}. Like the fidelity, the trace-norm distance is invariant under unitary transformation. Furthermore, it is contractive under the action of quantum processes,
\begin{align}
D(\mathcal{E}(\hat\rho_1),\mathcal{E}(\hat\rho_2)) \leq D(\hat\rho_1,\hat\rho_2).
\end{align}
The trace-norm distance relates to the fidelity according to the following bounds,
\begin{align}
1-F(\hat\rho_1,\hat\rho_2) \leq D(\hat\rho_1,\hat\rho_2) \leq \sqrt{1-F(\hat\rho_1,\hat\rho_2)^2}.
\end{align}
\comment{Add norm for channels}
\comment{Algebraic properties}

@@

\comment{To do! What is the composition of multiple squeezing operators? Multiplicative??}

@@

Note that lower bounds on fidelity, purity, efficiency and dephasing are all multiplicative on a scale of 0 to 1, and thus their logarithms may be regarded as cost metrics.

Spatio-temporal mode-mismatch, latency, dollar cost and displacements are clearly automatically metrics as they are additive.

>>>>

We define the fidelity of two processes, the process fidelity \index{Fidelity} \cite{bib:Gilchrist05}, to be the fidelity between two identical copies of a state that have been evolved under each of those processes, minimised over all possible states. That is, it provides a lower bound on the fidelity between identical states evolved under the two processes. In the context of networking, where quality must be guaranteed, this definition is more appropriate than, say, the average case fidelity. Specifically,
\begin{align}
\mathcal{F}(\mathcal{E}_1,\mathcal{E}_2) = \mathrm{tr}\left( \sqrt{\chi_1^{1/2}\cdot\chi_2\cdot\chi_1^{1/2}}\right),
\end{align}
where $\chi_1$ and $\chi_2$ are the process matrices\index{Process matrices} for $\mathcal{E}_1$ and $\mathcal{E}_2$.

@@

An alternate measure for the distance between two quantum states is the trace-norm distance\index{Trace-norm distance}, defined as,
\begin{align}
D(\hat\rho_1,\hat\rho_2) &= \frac{1}{2}\|\hat\rho_1 - \hat\rho_2\|_1 \nonumber\\
&= \frac{1}{2}\sum_i |\lambda_i|,
\end{align}
where $\lambda_i$ are the eigenvalues of \mbox{$\hat\rho_1-\hat\rho_2$}. Like the fidelity, the trace-norm distance is invariant under unitary transformation. Furthermore, it is contractive under the action of quantum processes,
\begin{align}
D(\mathcal{E}(\hat\rho_1),\mathcal{E}(\hat\rho_2)) \leq D(\hat\rho_1,\hat\rho_2).
\end{align}
The trace-norm distance relates to the fidelity according to the following bounds,
\begin{align}
1-F(\hat\rho_1,\hat\rho_2) \leq D(\hat\rho_1,\hat\rho_2) \leq \sqrt{1-F(\hat\rho_1,\hat\rho_2)^2}.
\end{align}

@@

Similarly, from the definition of the squeezing operator,
\begin{align}\label{eq:sq_op}
\hat{S}(\xi) = \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
it is evident that squeezing accumulates additively as well,
\begin{align}
\hat{S}(\xi_1)\hat{S}(\xi_2) = \hat{S}(
\xi_1+\xi_2).	
\end{align}

@@

Note that lower bounds on fidelity, purity, efficiency and dephasing are all multiplicative on a scale of 0 to 1, and thus their logarithms may be regarded as cost metrics. Spatio-temporal mode-mismatch, latency, dollar cost and displacements are clearly automatically metrics as they are additive.

### 2018-08-23 Sections/errors_in_quantum_networks.tex
squeezing

In the case of the displacement operation, which is implemented by mixing a state with a coherent state on a beamsplitter, errors in the amplitude of the coherent state or in the beamsplitter reflectivity will introduce an offset in the displacement amplitude. Thus, instead of implementing $\hat{D}(\alpha)$, we might over- or under-displace the state, implementing \mbox{$\hat{D}(\Delta)\hat{D}(\alpha)\propto \hat{D}(\alpha+\Delta)$}, for some error $\Delta$.

>>>>

In the case of the displacement operation, which is implemented by mixing a state with a coherent state on a beamsplitter, errors in the amplitude of the coherent state or in the beamsplitter reflectivity will introduce an offset in the displacement amplitude. Thus, instead of implementing $\hat{D}(\alpha)$, we might over- or under-displace the state, implementing,
\begin{align}
	\hat{D}(\Delta)\hat{D}(\alpha)\propto \hat{D}(\alpha+\Delta),
\end{align}
for some error $\Delta$.
